Achieving maximum possible precision on stellar radial-velocity measurements in multi-epoch spectroscopy

### 2017-12-01 paper/paper.tex
math typo

\newcommand{\unit}[1]{\mathrm{#1}}
\newcommand{\km}{\unit{km}}
\newcommand{\m}{\unit{m}}
\newcommand{\s}{\unit{s}}
\newcommand{\kms}{\km\,\s^{-1}}
\newcommand{\ms}{\m\,\s^{-1}}
\newcommand\todo[1]{\textcolor{red}{#1}}  % gotta have \usepackage{xcolor} in main doc or this won't work
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\HARPS}{\project{\acronym{HARPS}}}
\newcommand{\RV}{\acronym{RV}}
\newcommand{\CRLB}{\acronym{CRLB}}
\newcommand{\EPRV}{\acronym{EPRV}}

@@

In particular, the \CRLB\ is related to the Fisher Information that is
frequently used in cosmological experiment forecasts (\todo{CITE
  SHIT}).
It is that the \emph{inverse variance} $\sigma_v^{-2}$ of any velocity
estimator must be larger than the second derivative of the
\emph{negative} log likelihood function.
In equations:
\begin{eqnarray}
\frac{1}{\sigma_v^2} &\geq& \frac{d^2}{d_v^2}(-\ln L)
\end{eqnarray}

>>>>

\newcommand{\unit}[1]{\mathrm{#1}}
\newcommand{\km}{\unit{km}}
\newcommand{\m}{\unit{m}}
\newcommand{\s}{\unit{s}}
\newcommand{\kms}{\km\,\s^{-1}}
\newcommand{\ms}{\m\,\s^{-1}}
\newcommand{\todo}[1]{\textcolor{red}{#1}}  % gotta have \usepackage{xcolor} in main doc or this won't work
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\HARPS}{\project{\acronym{HARPS}}}
\newcommand{\RV}{\acronym{RV}}
\newcommand{\CRLB}{\acronym{CRLB}}
\newcommand{\EPRV}{\acronym{EPRV}}
\newcommand{\dd}{\mathrm{d}}

@@

In particular, the \CRLB\ is related to the Fisher Information that is
frequently used in cosmological experiment forecasts (\todo{CITE
  SHIT}).
It is that the \emph{inverse variance} $\sigma_v^{-2}$ of any velocity
estimator must be smaller than the second derivative of the
\emph{negative} log likelihood function:
\begin{eqnarray}
\frac{1}{\sigma_v^2} &\geq& \frac{\dd^2}{\dd v^2}(-\ln L)
\end{eqnarray}
